---
title: "Bobcat and coyote"
format: html
editor: visual
---

## Load libraries
```{r}
library("readr")
library("ggplot2")
library("sf")
library("dplyr")
library("tmap")
library("lubridate")
library("tidyr")
library("move2")
library("units")
library("rnaturalearth")
```

## Load movebank studies
```{r}
all_studies <- movebank_download_study_info()
cc_studies <- movebank_download_study_info(license_type = "CC_0")
```

## Load data for the bobcat/coyote study
```{r}
movebank_download_study_info(study_id = 2636372210)$sensor_type_ids

data <- movebank_download_study(
  study_id = 2636372210,
  sensor_type_id = c("gps"),
  'license-md5'='2253e05d47fd240054a126f011845acf'
)
```

## What are the coyotes and what are the bobcats?

The individual_local_identifiers starting with NECOY are Coyotes and the ones 
starting with MVBOB are bobcats.

```{r}
data <- data |> 
  mutate(animal_type = substr(individual_local_identifier, 1, 5))
```

## Plotting all data
```{r}
ggplot() +
  geom_sf(
    data = mt_track_lines(data),
    aes(color = "all") # This column does not exist, aggregating all data
  ) +
  labs(
    color = "Animal trails",
    title = "Zoomed-in view of data location"
  )
```

## Plotting by animal type
```{r}
tracks <- mt_track_lines(data)
tracks <- tracks |> 
  mutate(animal_type = substr(individual_local_identifier, 1, 5))
ggplot() +
  geom_sf(
    data = tracks, 
    aes(color = animal_type)
  ) +
  labs(
    color = "Animal trails",
    title = "Individual trails per animal type"
  )
```

## Net displacement analysis

Visualize the distance to the first location of each trajectory:

```{r}
displacement_data <- data |>
  mutate(track_id = mt_track_id(data)) |>
  group_by(track_id) |>
    mutate(displacement = c(st_distance(
    !!!syms(attr(data, "sf_column")),
    (!!!syms(attr(data, "sf_column")))[row_number() == 1]
  )))

displacement_data |> ggplot() +
  geom_line(aes(
    x = timestamp,
    y = set_units(displacement, "km"),
    color = track_id
  )) +
  ylab("Distance from start") +
  theme_linedraw()
```



## On a base map

```{r}
sf <- st_as_sf(data, coords = c("location-long", "location-lat"), crs = 4326, remove = FALSE)
#sf <- st_transform(sf, 2056)
mcp <- st_convex_hull(sf)
#plot(mcp)

tmap_mode("view")
tmap_options(basemaps = "OpenStreetMap")
tm_shape(sf) +
  tm_dots(size = "sensor_type_id")
```

